Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-13 paper.tex
Find reference for stronger tip vortices at lower Re
Add citation for Re definition

Scaled physical models are often used in science and engineering to approximate
real-world systems. The principle of dynamic similarity allows for geometrically
scaled systems to be dynamically identical if certain nondimensional physical
parameters are matched. In the case of fluid systems, the most important
nondimensional parameter is often the Reynolds number, $Re$, which quantifies
the importance of inertial forces over viscous forces on the flow physics: $Re
\equiv Ul/\nu$, where $U$ and $l$ are characteristic velocity and length scales,
respectively, and $\nu$ is the fluid kinematic viscosity. The other common
dynamical scale---for systems with a free surface---is the Froude number $Fr
\equiv U/\sqrt{gl}$, where $g$ is the gravitational acceleration. Matching both
Froude and Reynolds number is difficult for the same fluid, which is illustrated
by the relation $Re = l^{3/2} g^{1/2} Fr / \nu$, since $Re$ scales linearly with
$l$, or the geometric scale. In general the geometric scale of a physical model
is not necessarily the same as its dynamical scale. As such, hereafter we will
use the word ``scale'' to refer to this dynamical scale or Reynolds number and
assume Froude number is small enough to be negligible.

@@

We expect that lower lift on the blades at lower $Re$ will weaken tip vortex
shedding, and decrease the levels of turbulence shed from the blade boundary
layers. As mentioned previously, the dynamic stall vortex shedding is not
expected to be highly sensitive to Reynolds number, though a larger separation
bubble at lower $Re$ may induce higher levels of turbulence as shed vortices
become unstable and break down.

>>>>

Scaled physical models are often used in science and engineering to approximate
real-world systems. The principle of dynamic similarity allows for geometrically
scaled systems to be dynamically identical if certain nondimensional physical
parameters are matched. In the case of fluid systems, the most important
nondimensional parameter is often the Reynolds number, $Re$, which quantifies
the importance of inertial forces over viscous forces on the flow physics
\cite{Acheson1990}: $Re \equiv Ul/\nu$, where $U$ and $l$ are characteristic
velocity and length scales, respectively, and $\nu$ is the fluid kinematic
viscosity. The other common dynamical scale---for systems with a free
surface---is the Froude number $Fr \equiv U/\sqrt{gl}$, where $g$ is the
gravitational acceleration. Matching both Froude and Reynolds number is
difficult for the same fluid, which is illustrated by the relation $Re = l^{3/2}
g^{1/2} Fr / \nu$, since $Re$ scales linearly with $l$, or the geometric scale.
In general the geometric scale of a physical model is not necessarily the same
as its dynamical scale. As such, hereafter we will use the word ``scale'' to
refer to this dynamical scale or Reynolds number and assume Froude number is
small enough to be negligible.

@@

Despite lower lift on the blades at lower $Re$, we expect stronger tip vortex
shedding \cite{Yoon2005}. As mentioned previously, the dynamic stall vortex
shedding is not expected to be highly sensitive to Reynolds number, though a
larger separation bubble at lower $Re$ may induce higher levels of turbulence as
shed vortices become unstable and break down.
